\specialchapter{Acknowledgements}
%Font "test";  路路test路路; ``test"; ``test'': \texttt{texttt}; \textsl{textsl}; \emph{emph}; \textsc{textsc}; \textsf{textsf}; \textit{textit}
The ``crowd-sourced fog'' idea that is explained in this white paper has evolved and been practised for over five years. I rejoice that the number of its direct and indirect contributors has grown so great that the full recognition of all people who have made it possible is regretfully impractical. 

I first thank my advisor, Professor S.-H. Gary Chan, for his years of mentoring and encouragement. I have learned from him how to define, decouple, differentiate, develop and defend problems and ideas. From him, I have gained the habit of being systematic, structural, punctual and precise. I am also very grateful for his recommendation of me to the Technology Leadership and Entrepreneurship (TLE) program. 

Stone Huang at Tencent Cloud, has provided wise counsel throughout the evolution of this work since the very beginning. I am grateful to Zhi Wang and Wen Hu for the inspiring collaboration at the Tsinghua-Tencent Joint Laboratory for Internet Innovation Technology and to Wenwu Zhu for his advice. I thank Les Peng and Isco Wei at the Tencent Social Network Group (SNG) for their technical support. I thank many others at Tencent Technology and Engineering Group (TEG) for their roles in deploying code and providing data, as well as people I worked with at other organisations who were a source of inspiration for this project.  
%All my previous working experiences with respective institutions constituted a source of inspiration for this project. 

I am grateful for the support from the Hong Kong University of Science and Technology (HKUST) in its unwavering commitment to excellence in teaching, learning and research, especially its vision for future entrepreneurship education. Thanks to the School of Engineering, which conducts the TLE program and practises future-oriented educational experiments. Thanks to the School of Business and Management, where I attended some ``secret-weapon'' MBA courses, learned some practical business problem-solving skills and then reversely applied them to help analyse some technological problems. 

I acknowledge my teachers and colleagues who provided such supportive and stimulating environments, especially King Lun Yeung, Margaret Chau, Wendy Yau, Jenny Chan and Louise Yap at the Office of the Dean of Engineering and the TLE program, Qiang Yang of the Department of Computer Science and Engineering, Laurence C Franklin of the Department of Finance and the MBA program, as well as Sam Garg of the Department of Management. 

I am indebted to Mitchell M Tseng for encouraging me to do a real start-up, to Terrence F Yee for helping me sort out some IP issues, and to Claudia J Xu and Brian Sze for helping us receive some government funding through HKUST. 

I especially want to thank Tony Zhang, the co-founder and ex-CTO of Tencent, for pointing out the ``dominant battlefield'' of the Fog, and John Lu of the Tencent Video team, for helping polish the ideas and direct the project to a key problem related to a better ``carrier''. 

I want to express my gratitude to Po Chi Wu, who has given helpful suggestions and allowed our project to be case-studied in a business course. 

I appreciate the lessons learned from many friends, who did start-ups, organised influential competitions, or administrated laboratories. They include Hamza Zia (Parle), Pili Hu (Initium Media), Peter Chung (CSE Office and HackUST), Wen Huang (MTrec Lab. and AnanFlow), Francis Kwok (RADICA Systems) and Michael Huang (Maichuang Networks and ViewCloud). 

I am obliged to Yuqing Lin, Michael Xue and Cindy Liang at Lenovo Capital, for their insightful comments on improving this work. I am grateful for Camden Meek's and Ted Spaeth's help in document editing.  

The collaborators in the Pear Team --- Ian Mei, Yongming Li, Pearl Shu and Evian Ling, who also have my gratitude. Through collaborative work, I am able to understand what kind of people a start-up should look for. I also want to thank Raymond, Michael, Hammad, Gavin, Peipei, Shuya and July, who helped enhance Pear's capabilities and avoid risks in different dimensions. 

I owe thanks to Yolanda Yang, Gordon Yen and Derek Liu for many interesting discussions, and to the anonymous referees for many helpful suggestions.

Last but not least, I thank my parents, for their full support for my projects and the start-up company. I affectionately dedicate this white paper to them. 

